Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-20 paper/paper.tex
pass on differential testing

\emph{Results.}~We considered the following engines--Apple, Google,
Microsoft, and Mozilla. Figure~\ref{fig:summary} shows the breakdown
of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}). Additionally, each stacked bar breaks
down the bugs per status (\eg{}, ``1-New''). The prefix number
indicates the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already. Note that most
of these bugs affected two engines--Microsoft's \chakra{} and Apple's
\jsc{}.  We reported \noBugsBugsReportedGoogle{} bugs in Google
\veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
Mozilla's \smonkey{}.  Furthermore, our results show that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Considering cost per bug found, we found that test
transplantation, compared to differential testing, demanded less
effort from the developers who inspected the alarms. Most of the bugs
we found are of moderate severity.

@@

\vspace{1ex} To sum, the paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

@@

@@

This section describes the infrastructure we used for cross-engine
differential testing. Figure~\ref{fig:workflow} illustrate the
workflow of the approach. It takes on input a list of JS files and
generates warnings on output. Boxes in the figure denote
encapsulation, arrowed lines denote data flow, and the cycle icons
denote repetition--the leftmost icon indicates that each file in the
input list will be analyzed in separate whereas the rightmost icon
shows that a single file will be fuzzed multiple times.  The
bug-finding process works as follows. New inputs are obtained for a
given test input using some off-the-shelf input fuzzer;
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure ignores the input. Otherwise, it considers the input as
potentially fault-revealing; hence, interesting for human
inspection. The infrastructure uses the
open-source tool eshost-cli~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.\Mar{any difference in
  output is considered for reporting? are there any
  filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
  nao estamos mais utilizando isso devido a essa ferramenta nao 
  capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
  A respeito de filtros nos reports, nao. Nos so capturamos o output,
  o que modificamos eh apenas a formatacao do output para coletar apenas a
  mensagem e nao o stack trace.
  }

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

It is worth noting that a number of reasons exist, other than a bug,
to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
and ~\ref{tab:false-positives}) and there is no clear automatic
approach to precisely distinguish false and true positives. As such, a
human needs to inspect the warning to classify the issue. As mentioned
earlier, this justifies why differential testing is challenging to
automate at the functional level. To facilitate inspection, we
prioritized warnings and clustered them in groups. We describe these
strategies in the following.

\subsection{Prioritization}

>>>>

\emph{Results.}~We considered the following engines--Apple, Google,
Microsoft, and Mozilla. Figure~\ref{fig:summary} shows the breakdown
of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}). Additionally, each stacked bar breaks
down the bugs per status (\eg{}, ``1-New''). The prefix number
indicates the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already. Note that most
of these bugs affected two engines--Microsoft's \chakra{} and Apple's
JavaScriptCore (\jsc{}).  We reported \noBugsBugsReportedGoogle{} bugs in Google
\veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
Mozilla's \smonkey{}.  Furthermore, our results show that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Considering cost per bug found, we found that test
transplantation, compared to differential testing, demanded less
effort from the developers who inspected the alarms. Most bugs
we found are of moderate severity.

@@

\vspace{1ex} To sum, this paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

@@

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \vspace{-5ex}  
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
  \vspace{-2ex}
\end{figure}

@@

This section describes the infrastructure we used for cross-engine
differential testing. Figure~\ref{fig:workflow} illustrates the
workflow of the approach. It takes on input a list of JS files and
generates warnings on output. Numbered boxes in the figure denote the
data processors and arrowed lines denote data flows. The cycle icons
indicate repetition--the leftmost icon indicates that each file in the
input list will be analyzed in separate whereas the rightmost icon
shows that a single file will be fuzzed multiple times.

The bug-finding process works as follows. For a given test input, the
toolchain produces new inputs using some off-the-shelf input fuzzer
(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
selected.)  Then, the oracle checks whether or not the output produced
for the fuzzed file is consistent across all engines (step 2). In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure ignores the
input. Otherwise, it considers the input as potentially
fault-revealing; hence, interesting for human inspection. Finally, to
facilitate the human inspection process, the infrastructure
prioritizes warnings and clusters them in groups (step 3). We describe
these features in Sections~\ref{sec:prioritization} and
\ref{sec:clusterization}. Note that a number of reasons exist, other
than a bug, to explain discrepancy (see
Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}) and there is no clear automatic approach
to precisely distinguish false and true positives. As such, a human
needs to inspect the warning to classify the issue. As mentioned
earlier, this justifies why differential testing is challenging to
automate at the functional level.

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes. As such, we forked the
eshost-cli GitHub project and implemented that functionality on it. It
is also important to note that our checker does not support the case
where the test fails in all engines but the kind of failure (\eg{},
exception thrown) is different. Currently, our infrastructure does not
report discrepancy for that case. For that, it would be necessary to
properly parse the error message to retrieve the error types. We left
that as future work as we already found several discrepancies even
without that.

%% \Mar{any difference in
%%   output is considered for reporting? are there any
%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
%%   mensagem e nao o stack trace.
%%   }

\subsection{Prioritization}
\label{sec:prioritization}
